### 2018-06-22 Manuscripts/cog-psych/revision/methods_results_e3.tex
Working on fitting models to maximise correlations, but is slow. Unfeasible with multiple models. Somewhat optimised code still takes ages - I think I will need to restructure the script completely.

% \documentclass[12pt]{article} \usepackage[letterpaper, margin=1in,
% headheight=15pt]{geometry} \usepackage{amsmath, listings}

% \begin{document}

\section{Participants, Materials, and Procedure}

@@

\section{Results}

Overall accuracy of the participants was high, with a mean error rate of $.19$
($SD = .19$).

[Place error curve plots here, not unlike what NGPMG1994 has done]

[Move on to modelling analyses. Include correlation plots, don't worry about
individual fits. Also include the varying of PACKER's performance (and maybe
representativeness?) on correlation with changing tradeoff. ]

>>>>

% \documentclass[12pt]{article} \usepackage[letterpaper, margin=1in, %
%headheight=15pt]{geometry} \usepackage{amsmath, listings}

% \begin{document}
\section{Experiment 3.}

[I'm assuming Joe will include some preamble for the experiment, but otherwise
it should be fairly straightforward for me to churn out one anyway.]

\subsection{Participants, Materials, and Procedure}

@@

\subsection{Results}

Overall accuracy of the participants was high, with a mean error rate of $.19$
($SD = .19$). Error rates for each block are presented in Figure
\ref{fig:learningcurve}.

\begin{figure}
    \begin{center}
    \includegraphics[width=\textwidth/2]{figs/e3-learningcurve.pdf}
    \caption{Average error rate for each successive block. Green discontinuous
      line represents the overall mean error rate.}
    \label{fig:learningcurve}
    \end{center}
\end{figure}

In the previous section (or Section X.X), we demonstrated that the best
performing models were the two contrast models. In this section, our goal is to
investigate if contrast is also important in category learning tasks.

It is also the
goal of this paper to demonstrate that there is an association between the
model's [justifying the errorvscat plot is harder than I thought] To compare the
performances of each model, we analysed the correlation between each model's fit
to a participant's unique category set and the participant's error rate.
Intuitively, a well-performing model should be able to closely fit (i.e., easily
generate) A positive correlation would indicate that the model is We used the
same set of optimised parameters found from Section X.X, with individual values
for selective attention.

\begin{figure}
    \begin{center}
    \includegraphics[width=\textwidth]{figs/perror_corr.pdf}
    \caption{Correlation between observed participant error and model fit.}
    \label{fig:perror_corr}
    \end{center}
\end{figure}

To emphasize the strong influence of contrast in maximizing the association
between category generation and category learning, we computed the correlations
over wide range of $\theta_{contrast}$ values, with the other parameter values of
PACKER held constant at their optimized levels. As presented in Figure
\ref{fig:packer-corr}, the correlation quickly increases with increasing weight
on contrast, reaching a plateau above values of around 4.0.

\begin{figure}
    \begin{center}
    \includegraphics[width=0.8\textwidth]{figs/packer-corr.pdf}
    \caption{Correlation between PACKER's fit and participant error as a
      function of the $\theta_{contrast}$ parameter. To facilitate comparison,
      PACKER's other parameters ($c$, $\theta_{target}$) were set to the best
      fitting values obtained for copy-and-tweak in Table
      \ref{table:global-model-fits}. Grey dashed line represents the correlation
      between Copy \& Tweak's fit and participant error.}
    \label{fig:packer-corr}
    \end{center}
\end{figure}

The specific reason for why contrast as implemented in PACKER is superior to
contrast as implemented in the representativeness model is still not clear.

### 2018-06-22 Manuscripts/model-descriptions/jern-kemp-conjugate/representative.tex
Working on fitting models to maximise correlations, but is slow. Unfeasible with multiple models. Somewhat optimised code still takes ages - I think I will need to restructure the script completely.

\section*{Updated Version of the Jern \& Kemp (2013) Model}

Working backwards, what is needed for simulation of exemplar generation is the probability of generating a stimulus $y$ given exposure to members of the target category $x_B$:
\
\begin{equation}
p(y | x_B) = ?
\end{equation}
\
where $x_B$ may be empty. Jern \& Kemp's model achieves this using a generative process. Category members ($x_A$ or $x_B$; more generally written as $x_C$) are assumed to have been generated using an underlying category distribution (specifically, multivariate normal):
\
\begin{equation}
  x_C \sim Normal(\mu_{C}, \Sigma_{C})
\end{equation}
\
$p(y | x_C)$ is proportional to the candidate's density under the target category's distribution. Thus, obtaining the category distribution parameters $(\mu_{C}, \Sigma_{C})$ is key for generation. This document describes how we compute these variables in a conjugate model.

@@

In the case of a populated class, $\mu_{C}$ ends up lying somewhere between $\mu_{0}$ and $\bar{x_C}$, depending on $\kappa_{0}$ and $n_C$. In the case of an empty class, $n_C = 0$, Equation \ref{eq:category_mus} reduces to $\mu_{C} = \mu_{0}$. Because we set $\mu_0$ to the center of the space, this outcome is the same as if we had integrated over all possible $\mu_C$. In practice, if $n_C = 0$, the model picks a stimulus at random from all candidates (uniform probabilities).

@@

\
\begin{equation}
    \Sigma_D = \Sigma_0 + \sum_{C}{C_C}
\end{equation}
\
$\Sigma_{0}$ is a $p$-by-$p$ prior covariance matrix. We use a $p$-dimensional identity matrix $I_p$ multiplied element-wise against a free parameter, $\rho$, controlling the amount of variance assumed by the prior:
\
\begin{equation}
    \Sigma_0 =  I_p\rho
\end{equation}

Thus, categories are assumed to have some degree of variance along each feature (specified by $\rho$), but not are assumed to possess feature-feature correlations.

@@

\begin{equation}
  \Sigma_C = [\Sigma_D\nu + C_C +
    \dfrac
    {\kappa n_C}
    {\kappa + n_C}
    (\bar{x_C}-\mu_C)(\bar{x_C}-\mu_C)^T
  ] (\nu + n_C)^{-1}
  \label{eq:Sigma_y}
\end{equation}
\
$\kappa$, $\bar{x_C}$, $C_C$, $n_C$, $\mu_0$,  are the same values as described above. $\nu$ is an additional free parameter, weighting the importance of $\Sigma_{D}$. $\nu$ must be greater than $p-1$. When $x_b$ is empty, Equation \ref{eq:Sigma_y} reduces to $\Sigma_C = \Sigma_D$.

@@

$x$ are assumed to be drawn from a the distribution given by $Normal(\mu_{C}, \Sigma_{C})$. Thus,

\begin{equation}
  p(y) \propto Normal(y; \mu_{C}, \Sigma_{C})
\end{equation}

In practice, $p(y)$ is computed by first obtaining the relative density of every possible generation candidate $y_i$ under the category distribution. The end probability is a normalization of these values:

\begin{equation}
  p(x) = \dfrac
    {exp( \theta Normal(y ; \mu_{C}, \Sigma_{C}))}
    {\sum_i exp( \theta Normal(y_i ; \mu_{C}, \Sigma_{C}))} 
\end{equation}
\
where $\theta$ is a response determinism parameter.

@@

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item $\kappa$. Scalar, $\kappa>0$. Weights the importance of $\mu_{0}$ in inferring category $\mu_{C}$.
    \item $\rho$. Scalar, $\rho>0$. Sets the assumed variance in the domain prior, $\Sigma_{0}$.
    \item $\nu$. Scalar, $\nu > p-1$. Weights the importance of $\Sigma_{D}$ in inferring the domain $\Sigma_{C}$.
    \item $\theta$. Scalar, $\theta > 0$. Response determinism parameter.
\end{itemize}

>>>>

\section*{Conjugate Implementation of the Jern \& Kemp (2013) Model with Representativeness}

The representativeness model is very similar to the Jern \& Kemp (2013)
hierarchical Bayesian model. The essential difference here is the ultimate
formulation of response probabilities. Where in the original hierarchical
Bayesian model the exemplars are drawn from Gaussian distributions, in the
representativeness model each exemplar is drawn in proportion to the exemplar's
representativeness. The representativeness of an exemplar is defined by
Tenenbaum and Griffiths (2012) as the relative evidence that is provided by the
exemplar $x$ for a given hypothesis $h$ compared to all other hypotheses $h'$:

\begin{equation}
  R(x,h) = \log \dfrac{p(x|h)}{\sum_{h'\neq h}{p(x|h')p(h')}}
\label{representativeness}
\end{equation}

For simplicity, and consistency with the original hierarchical Bayesian model,
we define $h_{C}$ as a multivariate normal distribution for a particular
category $C$ parameterised by $\mu_C$ and $\Sigma_C$. For completeness, this
document will repeat some information from the hierarchical Bayesian model
document and describee how we compute these variables.

@@

In the case of a populated class, $\mu_{C}$ ends up lying somewhere between $\mu_{0}$ and $\bar{x_C}$, depending on $\kappa_{0}$ and $n_C$. In the case of an empty class, $n_C = 0$, Equation \ref{eq:category_mus} reduces to $\mu_{C} = \mu_{0}$. Because we set $\mu_0$ to the center of the space, this outcome is the same as if we had integrated over all possible $\mu_C$.

In practice, if $n_C = 0$, the model picks a stimulus at random from all candidates (uniform probabilities).

@@

\
\begin{equation}
    \Sigma_D = \Sigma_0 + \sum_{C}{C_C}
\end{equation}
\
$\Sigma_{0}$ is a $d$-by-$d$ prior covariance matrix. We use a $d$-dimensional identity matrix $I_d$ multiplied element-wise against a free parameter, $\lambda$, controlling the amount of variance assumed by the prior:
\
\begin{equation}
    \Sigma_0 =  \lambda I_d
\end{equation}

Thus, categories are assumed to have some degree of variance along each feature (specified by $\lambda$), but not are assumed to possess feature-feature correlations. Differences in the assumed variance among the features, similarly to weighting in an exemplar model, can be implemented through a small change to the equation. Specifically, the variance assumed of dimension $k$ is given by:
\
\begin{equation}
    \Sigma_{0k} =  \lambda w_k d
\end{equation}
\
where $d$ is the number of dimensions, and $w_k$ ($0 \leq w_k \geq 1$, $\sum_k{w_k} = 1$) indicates the dimension's relative share of the total assumed variability. Under this system, evenly distributed weights result in uniformly assumed variances, equal to $\lambda$.

@@

\begin{equation}
  \Sigma_C = [\Sigma_D\nu + C_C +
    \dfrac
    {\kappa n_C}
    {\kappa + n_C}
    (\bar{x_C}-\mu_C)(\bar{x_C}-\mu_C)^T
  ] (\nu + n_C)^{-1}
  \label{eq:Sigma_y}
\end{equation}
\
$\kappa$, $\bar{x_C}$, $C_C$, $n_C$, $\mu_0$,  are the same values as described above. $\nu$ is an additional free parameter, weighting the importance of $\Sigma_{D}$. $\nu$ must be greater than $d-1$. When $x_b$ is empty, Equation \ref{eq:Sigma_y} reduces to $\Sigma_C = \Sigma_D$.

@@

As mentioned earlier, this is the point where the representativeness model
diverges from the hierarchical Bayesian model. Specifically, the probability of
generating exemplar $x$ is proportional to its representativeness:

\begin{equation}
  p(x) \propto R(x,h) ,
\end{equation}
where $h$ is a multivariate normal distribution parameterised by $\mu_{C}$ and
$\Sigma_{C}$.

In practice, $p(x)$ is computed by first obtaining the representativeness of
every possible generation candidate $x_i$. The end probability is a
normalization of these values:

\begin{equation}
  p(x) = \dfrac
    {\exp( \theta \cdot R(x,h))}
    {\sum_i \exp( \theta \cdot R(x_i,h_i))} 
\end{equation}
\
where $\theta$ is a response determinism parameter.

@@

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item $\kappa$. Scalar, $\kappa>0$. Weights the importance of $\mu_{0}$ in inferring category $\mu_{C}$.
    \item $\lambda$. Scalar, $\lambda>0$. Sets the assumed variance in the domain prior, $\Sigma_{0}$.
    \item $\nu$. Scalar, $\nu > d-1$. Weights the importance of $\Sigma_{D}$ in inferring the domain $\Sigma_{C}$.
    \item $\theta$. Scalar, $\theta > 0$. Response determinism parameter.
\end{itemize}
